An Efficient Calculus for Generalised Parikh Images of Regular Languages

### 2022-06-13 main.tex
Dagens text

To generalise the calculus to calculations on products of automata, we change the main predicate to take arbitrarily many automata:
\begin{definition}
  $\ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}$
  is true exactly when the single-automaton version of the predicate would hold
  for the automaton.

\end{definition}

  First we extend $\Expand$ to generate flow equations and instances of $\Connected$ for each automaton:
  \begin{mathpar}
    \inferrule*[left=ExpandM]
      {\Set{\FlowEq(\Automaton_i), \Connected(\Automaton_i) \SuchThat \Automaton_i \in \Automaton_1,\ldots,\Automaton_k}, \ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
      {\ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
  \end{mathpar}

@@

Then we introduce the rule $\Materialise$, used to compute a partial product between two terms:
\begin{mathpar}
  \inferrule*[left=Materialise,right=\textnormal{where $\Automaton' = \Automaton_1\times\Automaton_2$}]
    {    \BindingSum(\Automaton', \Filter),\ImagePredicate{\Automaton'\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
    {\ImagePredicate{\Automaton_1\times\Automaton_2\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
\end{mathpar}

>>>>

To generalise the calculus to calculations on products of automata, we change the main predicate to take arbitrarily many automata:
\begin{definition}
  $\ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}$
  is true exactly when the single-automaton version of the predicate would hold
  for the automaton.
\end{definition}

  For the calculus, we first extend $\Expand$ to generate flow equations and instances of $\Connected$ for each automaton.

      % EXPAND
      \ExpandM & 
      \inferrule
      {\Set{\FlowEq(\Automaton_i), \Connected(\Automaton_i) \SuchThat \Automaton_i \in \Automaton_1,\ldots,\Automaton_k}, \ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
      {\ImagePredicate{\Automaton_1\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause} & 
      None \\
      \Materialise &
      \inferrule
      {    \BindingSum(\Automaton', \Filter),\ImagePredicate{\Automaton'\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause}
      {\ImagePredicate{\Automaton_1\times\Automaton_2\times\ldots\times\Automaton_k}{\Map}{\Filter}{\MonoidElement}, \SomeInequalities, \SomeClause} &
      $\Automaton' = \Automaton_1\times\Automaton_2$ \\
      \bottomrule
      \end{tabular}
      \caption{Additional derivation rules for products of arbitrarily many automata.}\label{tbl:rules:multi}
    \end{table}

@@

Then we introduce the rule $\Materialise$, used to compute a partial product between two terms:
